Relationships in the extremes and their influence on competition and coexistence

### 2021-10-28 paper/Paper.Rnw
sentence in discussion
fixed parameter description in fig 2 caption

\underline{paragraph summarizing results of G2 and how it compares and builds on prior theory}
Furthermore, we have shown not only that is it possible to decompose storage effect into the effect of correlation \emph{per se} and the effect of ATAs, but this new term that holds the contribution of not only the correlation but the structure of the correlation is a non-negligible term, in the lottery model. Our result adds coexistence to the list of ecological theory/phenomena that ATAs have been found to be important for \citep{Ghosh_2020_AER, Ghosh_2020_Eco, Ghosh_2020_ecolevol, Ghosh_2021}. 
%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.

@@

\begin{figure}
\includegraphics[width=.75\textwidth]{../results_figs/fig2.pdf}
\caption{Our simulated lottery-model populations influenced by asymmetric tail associations (ATAs) recovered from low densities less often and 
spent more time in a state of one-species dominance, demonstrating that ATAs can influence aspects of 
species coexistence. Panel A shows species 1, from the lottery 
model subject to environmental noise with symmetric tail associations (Fig. \ref{fig:noise}B). Panel B shows species 1 from the 
same model with the same parameters, but subject to noise with left-tail association (Fig. \ref{fig:noise}A).
Both simulations were run for \Sexpr{M} time steps, though only the first $1000$ are shown. Periods of 
``noticeable coexistence'' of the species, defined to be periods when both species each comprise at least $5\%$ of 
total abundance, are marked in grey. The average duration of periods of noticeable coexistence 
was \Sexpr{fig2$coSym} time steps for panel A and \Sexpr{fig2$coATA} for panel B, over the full length of the simulations; 
whereas the average duration of periods of
one-species dominance was \Sexpr{fig2$domSym} time steps for panel A and \Sexpr{fig2$domATA} for B. Thus, while periods of 
noticeable coexistence were of similar duration for the two scenarios, periods of one-species dominance were much longer,
on average, for the ATA case. Parameters were $\mu_1 = \Sexpr{fig2$params[1]} + \Sexpr{fig2$params[1]}$ and $\mu_2 = \Sexpr{-(fig2$params[1])}$, $\delta = \Sexpr{fig2$params[2]}$, and $\sigma = \Sexpr{fig2$params[3]}$. See Introduction for model details. 
\label{fig:pedagog}}
\end{figure}
%***DAN: Dan has edited this caption

>>>>

\underline{paragraph summarizing results of G2 and how it compares and builds on prior theory}
Furthermore, we have shown not only that is it possible to decompose storage effect into the effect of correlation \emph{per se} and the effect of ATAs, but this new term that holds the contribution of not only the correlation but the structure of the correlation is a non-negligible term, in the lottery model. Our result adds coexistence to the list of ecological theory/phenomena that ATAs have been found to be important for \citep{Ghosh_2020_AER, Ghosh_2020_Eco, Ghosh_2020_ecolevol, Ghosh_2021}. Seemingly consistent with fluctuation dependent mechanisms, as \sigma increased, so did the the magnitudes of $\Delta_i^{[EC]}$ and $\Delta_i^{[E \nat C]}$.
%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.

@@

\begin{figure}
\includegraphics[width=.75\textwidth]{../results_figs/fig2.pdf}
\caption{Our simulated lottery-model populations influenced by asymmetric tail associations (ATAs) recovered from low densities less often and 
spent more time in a state of one-species dominance, demonstrating that ATAs can influence aspects of 
species coexistence. Panel A shows species 1, from the lottery 
model subject to environmental noise with symmetric tail associations (Fig. \ref{fig:noise}B). Panel B shows species 1 from the 
same model with the same parameters, but subject to noise with left-tail association (Fig. \ref{fig:noise}A).
Both simulations were run for \Sexpr{M} time steps, though only the first $1000$ are shown. Periods of 
``noticeable coexistence'' of the species, defined to be periods when both species each comprise at least $5\%$ of 
total abundance, are marked in grey. The average duration of periods of noticeable coexistence 
was \Sexpr{fig2$coSym} time steps for panel A and \Sexpr{fig2$coATA} for panel B, over the full length of the simulations; 
whereas the average duration of periods of
one-species dominance was \Sexpr{fig2$domSym} time steps for panel A and \Sexpr{fig2$domATA} for B. Thus, while periods of 
noticeable coexistence were of similar duration for the two scenarios, periods of one-species dominance were much longer,
on average, for the ATA case. Parameters were $\mu_1 = \Sexpr{fig2$params[1] + fig2$params[1]}$ and $\mu_2 = \Sexpr{-(fig2$params[1])}$, $\sigma = \Sexpr{fig2$params[2]}$, and $\delta = \Sexpr{fig2$params[3]}$. See Introduction for model details. 
\label{fig:pedagog}}
\end{figure}
%***DAN: Dan has edited this caption
